Hydras, Ordinals \& Co.\\ A library in Coq of entertaining formal mathematics

### 2021-10-20 doc/gaia-chapter.tex
add a new chapter (Gaia)
minor changes

@@

>>>>

\emph{The following definitions and lemmas are in
\href{../theories/html/gaia_hydras.T1Bridge.html}%
{\texttt{gaia\_hydras.T1Bridge}}}.

Since both libraries \texttt{gaia} and \texttt{hydra-battles} have their own type \texttt{T1}, we will work with the following notations.

\inputsnippets{T1Bridge/hT1gT1}

The bridge between both libraries is made of two functions.

@@

\inputsnippets{T1Bridge/iotaPiRw, T1Bridge/piIotaRw}

The functions \texttt{iota} and \texttt{pi} allow us to define
a notion of refinement for constants, functions, predicates and relations.

\inputsnippets{T1Bridge/refineDefs}
